\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{microtype}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\arabic{table}}
\newcommand{\Ind}{\ensuremath{\mathcal{I}}}

\title{\bfseries Supplementary Material\\[0.3em]
\large How Predictable Are Rare Precipitation Extremes?
A Calibration-Aware Assessment for London}
\author{Fankai Dong \and Olatunji Johnson}
\date{\today}

\begin{document}
\maketitle

\section{Results at the 99th-percentile threshold}
\label{sec:supp99}

The main paper analyses the $95$th-percentile index, which has $417$ extreme days
($287$ train, $130$ test). The $99$th-percentile index is far scarcer --- only
$137$ extreme days in thirty years ($101$ train, $36$ test) --- which precludes
the held-out intensity analysis (that requires extreme days in both train and
test across several splits). For completeness we report here the
\emph{occurrence} results of the simpler models at the $99$th percentile; the
deep Gaussian-process extreme-value hurdle, already dominated at the $95$th
percentile, is not re-run.

Table~\ref{tab:supp99} shows the bake-off (seed-averaged over three seeds, horizon
$h=1$), scored against climatology as in the main paper. The qualitative picture
matches the $95$th percentile but is weaker and noisier, as expected with a third
as many events:
\begin{itemize}
\item \textbf{Occurrence remains weakly predictable.} A plain calibrated logistic
regression with the ERA5 drivers beats climatology (Brier skill score
$+0.015$), improving on index history alone ($+0.001$); the gain again comes
chiefly from the convective-instability and circulation fields. Resolution
(informativeness) is positive but smaller than at the $95$th percentile
($0.36\times10^{-3}$ versus $0.83\times10^{-3}$).
\item \textbf{The distributional models fall below climatology.} With only $101$
training exceedances, the zero-inflated gamma and eGPD regressions are slightly
worse than climatology on the Brier score, and the zero-inflated log-normal is
again catastrophically miscalibrated --- echoing, more sharply, the main-paper
finding that the response distribution matters and that data scarcity penalises
the more flexible models.
\item \textbf{The tail is climatology-bound.} No model beats the climatological
tail on the threshold-weighted CRPS (all skill scores $\le 0$), and the scarce
exceedances do not support the held-out intensity test.
\end{itemize}

\begin{table}[h]
\centering
\caption{Bake-off at the $99$th-percentile threshold (London, $h=1$,
seed-averaged). Brier skill score (BSS) and threshold-weighted CRPS skill
(twCRPSS) are relative to climatology; positive is better. RES is the Brier
resolution ($\times10^3$). Climatology and a stationary peaks-over-threshold
model define the reference. Compare with Table~2 of the main paper
($95$th percentile).}
\label{tab:supp99}
\begin{tabular}{lccc}
\toprule
\textbf{Model} & \textbf{BSS} & \textbf{RES}$\times10^3$ & \textbf{twCRPSS} \\
\midrule
Climatology / stationary POT     & $0.000$  & $0.00$ & $0.000$ \\
Logistic (index history)         & $+0.001$ & $0.08$ & --- \\
Logistic ($+$ERA5)               & $\mathbf{+0.015}$ & $0.36$ & --- \\
ZI gamma ($+$ERA5)               & $-0.069$ & $0.20$ & $-0.130$ \\
ZI extended-GPD ($+$ERA5)        & $-0.048$ & $0.26$ & $-0.087$ \\
ZI log-normal ($+$ERA5)          & $-1.153$ & $0.25$ & $-4.827$ \\
\bottomrule
\end{tabular}
\end{table}

In short, the $99$th-percentile threshold tells the same story as the $95$th ---
weak but genuine occurrence predictability led by convective instability, a
climatology-bound tail, and a penalty on over-flexible models --- but with too
few events to support the intensity analysis or to add to the main conclusions.

\end{document}
